\centering DAOSYS: Smart DAO Protocol for Decentralized Finance

### 2022-09-28 latex/whitepaper/article.tex
update minor fix

Currently, there are approximately 2,500 Masternodes running on the Syscoin network. In \cite{Moo22A}, we ran a case study with a five-year projection analysis on an additional 400 Masternodes, while at the same time factoring in network growth. We applied all these components into our model to estimate daily supply growth of the network, along with its respective confidence intervals; see Appendix \ref{sec:masternode_tokenomics} for details. Overall, we are predicting an overall return of 14.7M SYS which represents a five-year return of 36.8\% from the original investment of 40M SYS; see Fig. \ref{fig:reward_output}. Without DAOSYS, we would only realize an overall return of 31.2\%; for methodology see Appendix B. Keep in mind that the principle investment of 100K SYS is not subject to any risk, and the estimated DAOSYS returns is working from Masternode returns as its principle. With this tokenomics model, we estimated the expected share a typical node contributes to the network on a daily basis. Finally, with expected share, we estimated the five-year output of 400 new Masternodes; see Table \ref{table:mn_returns} for details.

>>>>

Currently, there are approximately 2,500 Masternodes running on the Syscoin network. In \cite{Moo22A}, we ran a case study with a five-year projection analysis on an additional 400 Masternodes, while at the same time factoring in network growth. We applied all these components into our model to estimate daily supply growth of the network, along with its respective confidence intervals; see Appendix \ref{sec:masternode_tokenomics} for details. Overall, we are predicting an overall return of 14.7M SYS which represents a five-year return of 36.8\% from the original investment of 40M SYS; see Fig. \ref{fig:reward_output}. Without DAOSYS, we would only realize an overall return of 31.2\%. Keep in mind that the principle investment of 100K SYS is not subject to risk as the estimated DAOSYS returns are utilizing Masternode returns as its principle. With this tokenomics model, we estimated the expected share a typical node contributes to the network on a daily basis. Finally, with expected share, we estimated the five-year output of 400 new Masternodes; see Table \ref{table:mn_returns} for details.
